---
title: "Portfolio MOdeling"
author: "Nittala Venkata Sai Aditya"
output: word_document
date: "2022-08-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Portfolio Modelling

We want to pick a diversified portfolio which can give all the different combinations of ETFs and you try to get the maximum return possible.

**Portfolio -1**
  
  **Scenario-1: Assign equal weights**
  
  * EQUITY ETFS

We want to experiment with picking Equity ETF first and seeing if they have any impact on the VAR. The idea is to analyse if just picking different kinds of large cap/mid cap or small cap funds in the Equity asset class has any bearing on the final Var.
The first portfolio consists of 3 large cap, 2 medium cap and 2 small cap and 1 multi cap equity ETF's. The aim is to see how the size of the assets have an impact on the overall VAR.

The following ETF's are part of portfolio - 1

* Vanguard (VOO) : This ETF tracks the S&P 500 Index, one of the most famous benchmarks in the world and one that tracks some of America’s largest companies. VOO is more diversified than most, containing just over 500 securities in total. As a result, this fund could serve as a building block for many portfolios making it an excellent choice for many buy and holders, especially for those looking to keep costs at a minimum. It also has a low expense ratio of 0.03%. It has a mix of technology, financial and electronic sector as well. Asset Cap - 273,793 millions

* Invesco QQQ Trust (QQQ) : This ETF offers exposure to one of the world’s most widely-followed equity benchmarks, the NASDAQ, and has become one of the most popular exchange-traded products. The significant average daily trading volumes reflect that QQQ is widely used as a trading vehicle, and less as a components of a balanced long-term strategy. This also is generally in the technological sector.
Asset Cap - 177,912 millions

* Shares Core S&P 500 ETF (IVV) : IVV has become one of the largest ETFs in the world, offering exposure to one of the world’s best-known and most widely followed stock indexes. This ETF tracks the S&P 500 Index, which includes many large and well known U.S. firms. It has a high P/E ratio and dividend along with a low expense ratio. Asset Cap - 308,926 millions

* iShares Core S&P Mid-Cap ETF (IJH) : This ETF is one of several ETFs available that offers exposure to mid cap U.S. stocks, an asset class that can make up a significant portion of long-term, buy-and-hold portfolios.The expense ratio is competitive with the other options out there. Finance and Producer Management are the more prevalent sectors

* Vanguard Mid-Cap ETF (VO) : VO offers exposure to a balanced portfolio of stocks, including close to 460 individual names and spreading exposure relatively evenly. The expense ratio is among the cheapest in the category making it an excellent choice for those looking to keep costs to an absolute minimum.

* Vanguard Small Cap Value ETF (VBR) : VBR seeks to replicate a benchmark which offers exposure small cap firms that exhibit value characteristics in the U.S. equity market. The investment thesis behind small caps is that these firms are likely to provide strong growth prospects to a portfolio and should have a much easier time growing then their large cap counterparts. 

* iShares Core S&P Small-Cap ETF (IJR) : This ETF is linked to an index which tracks the performance of small cap U.S. stocks. This fund will make for a good investment for traders looking for growth and are aware of the risks that come along with investing in a small cap ETF.

* SPDR S&P Dividend ETF (SDY) : This ETF is linked to the S&P High Yield Dividend Aristocrats Index, which offers exposure to dividend paying large-cap companies that exhibit value characteristics within the U.S. equity market.Only the highest yielding companies are chosen and these firms must have increased dividends every year for at least 25 consecutive years. Thanks to this focus, SDY only invests in companies that are most likely to continue to pay out dividends in the future making it a solid pick for dividend focused investors even if the diversification is a little lacking.


```{r 3a1, echo=FALSE, message=FALSE,warning=FALSE}
library(mosaic)
library(quantmod)
library(foreach)


stockList_p1 = c('QQQ','IVV','VOO','IJH','VO','VBR','SDY','IJR')

#Extract the data from the database
getSymbols(stockList_p1,from='2017-01-01')

for(ticker in stockList_p1) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
#Get Percentage close to close from previous day

all_returns = cbind(ClCl(QQQa),ClCl(IVVa),ClCl(VOOa),ClCl(IJHa),ClCl(VOa),ClCl(VBRa),ClCl(SDYa),ClCl(IJRa))

#,
all_returns = as.matrix(na.omit(all_returns))
#Remove the first column since it's current day - previous day. As a result we get na

pairs(all_returns)

N = nrow(all_returns)

```

* Most of the ETFs seem to be correlated since most of them belong to the same sectors where Technology is the main contributor.
* Most ETFs are not closely correlated with IJR since IJR has more of a financial sector background and also is a small cap.

```{r 3a2, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
plot(all_returns[1:(N-1),3], all_returns[2:N,3],xlab='Current Day Return',ylab='Previous Day Return',main = 'Current vs Previous Returns Relation for Vooa')
```
* The above plot shows that there is no correlation between current and yesterday's returns for a sample ETF which is on expected lines otherwise it would have been easy to predict and exploit the markets


```{r 3a3, echo=FALSE, message=FALSE,warning=FALSE}
 set.seed(1)
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.125,0.125,0.125,0.125,0.125,0.125,0.125,0.125)
	n_days = 20
	wealthtracker_p1 = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
	  holdings = weights * total_wealth
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker_p1[today] = total_wealth
	}
	wealthtracker_p1
}

hist(sim1[,n_days], 25,main = 'Histogram of returns for past 20 days for P1S1')


```
* The mean of the returns is plotted above and it can be seen that the mean is slightly beyond 100000 which was our initial amount

```{r 3a4, echo=FALSE, message=FALSE,warning=FALSE}
plot(wealthtracker_p1, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P1S1')
```
* The above plot shows the fluctuation in the wealth in the 20 day trading window. We see a small profit in all of the days and not a loss so that's a good measure of our portfolio.

```{r 3a5, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p1 = mean(sim1[,n_days] - initial_wealth)
cat('Mean of profits for P1S1is: ')
meanReturn_p1

```


```{r 3a6, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p1 = quantile(sim1[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 1 and scenario 1 is : ")
var_p1
```
```{r 3a7, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p1= sim1[,n_days]- initial_wealth
(hist(profit_p1,breaks = 30, main='Histogram of profits/Losses for P1S1',xlab="Profit"))
abline(v=var_p1,col="red",lwd=3)
abline(v=mean(profit_p1),col="blue",lwd=3)
text(-14700,400,"VAR Risk Line")
text(6500,700,"Mean Line")
```

* There's a 0.05 probability that we will lose the mention VAR score over the course of this 20 day window for our portfolio.

* Let's calculate the mean returns for all the columns and try to assign more weight to the higher returnees and lower weights to the lower returnee ETF's

* Let's look at the histogram distribution of the ETF's returns. 

```{r 3a8, echo=FALSE, message=FALSE,warning=FALSE}
all_returnsDf_p1 = as.data.frame(all_returns)
meanDf_p1 =  all_returnsDf_p1 %>% summarise_if(is.numeric, mean)
library(Hmisc)
hist.data.frame(all_returnsDf_p1)
```

* IJR has more returns followed by QQQ so we will assign more weights to these 2 and assign the least to VBR and IJH

```{r 3a9, echo=FALSE, message=FALSE,warning=FALSE}
unlistedDf_p1 = data.frame(score = unlist(meanDf_p1))

rowList_p1 = rownames(unlistedDf_p1)
newDf_p1 = as.data.frame(cbind(rowList_p1,unlistedDf_p1))
ggplot(newDf_p1,
            aes(x=rowList_p1,y=score)) +
 geom_bar(stat="identity") + ggtitle("ETF Returns for Portfolio -1") +
 xlab("ETF") + ylab("ETF Return Score")  

```

**Scenario-2: Assigning more weight to highe return ETF**

* Assign half weight to IJR and 0.2 to QQQ and least weight of 0.03 to VBR and IJH

```{r 3a10, echo=FALSE, message=FALSE,warning=FALSE}
set.seed(1)
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.200,0.06,0.06,0.03,0.06,0.03,0.06,0.5)
	n_days = 20
	wealthtracker_p1s2 = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
	  holdings = weights * total_wealth
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		wealthtracker_p1s2[today] = total_wealth
	}
	wealthtracker_p1s2
}

hist(sim1[,n_days], 25,main = 'Histogram of returns for past 20 days for P1S2')
```

```{r 3a11, echo=FALSE, message=FALSE,warning=FALSE}
plot(wealthtracker_p1s2, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P1S2')
```
* Mean of profits is more when we assign more weight to IJH. This could be due to the presence of more financial sector stocks and we recently had a boom coming out of covid for these stocks. As a result the returns are more for those ETF

```{r 3a12, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p1s2 = mean(sim1[,n_days] - initial_wealth)
cat('Mean of profits for P1S2 is: ')
meanReturn_p1s2
```
```{r 3a13, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p1s2 = quantile(sim1[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 1 and scenario 2 is : ")
var_p1s2
```

```{r 3a14, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p1s2= sim1[,n_days]- initial_wealth
(hist(profit_p1s2,breaks = 30, main='Histogram of profits/Losses for P1S2',xlab="Profit"))
abline(v=var_p1s2,col="red",lwd=3)
abline(v=mean(profit_p1s2),col="blue",lwd=3)
text(-14700,400,"VAR Risk Line")
text(6500,700,"Mean Line")
```
* Value of risk is more than the previous case since we bet more aggressively on one ETF.

**Portfolio-2**

**Scenario-1 : Distribute all funds equally**

* We will now create a portfolio with a mixture of Equity and Bond ETFs so that there is a bit more diversity in the asset classes.We will take 4 bond and 4 equity ETFs from the previous portfolio list

* Vanguard Total Bond Market ETF (BND) : This popular ETF offers exposure to entire investment grade bond market in a single ticker, with holdings in T-Bills, corporates, MBS, and agency bonds. This has the largest market capital and has a small expense ratio as well.

* iShares Core U.S. Aggregate Bond ETF (AGG) : The largest exchange-traded bond fund out there and one of the top 10 ETFs in the U.S. by assets, AGG boasts roughly $81 billion under management and is the simplest way to gain exposure to fixed-income markets. It is made up of more than 10,000 individual bond holdings to represent broad exposure to U.S. investment-grade bonds, including about 40% of its portfolio in U.S. Treasury bonds. The rest includes top-tier corporate bonds from firms like JPMorgan Chase & Co. (JPM) as well as mortgage-related debt. With loe expense ratio, AGG is a very affordable one-stop shop for bond exposure.

* Vanguard Short-Term Corporate Bond ETF (VCSH) : It is a $41 billion fund that focuses on high-quality corporate debt but with the typical bond in its portfolio maturing in just 2.8 years. That means investors can have a lot more certainty that those debts will be repaid in full, since it's a smaller window of time for unexpected disruptions to upend operations at these firms. The yield is a bit less than the longer-dated VCIT but is still very attractive when compared with the typical S&P 500 dividend stock – and offering a lot less risk, which is perhaps a big selling point all by itself in the current environment.

* iShares 20+ Year Treasury Bond ETF (TLT) : If you don't want to diversify into corporate debt and instead want the rock-solid comfort of the U.S. Treasury alone, perhaps the most popular low-risk way to play the bond market is TLT.The duration of this bond ETF's holdings are all 20 years or longer, which does provide some long-term interest rate risk; the fund is actually down 20% in the last 12 months as rates have moved higher and devalued its older positions. However, with a yield that is now roughly 60% higher than what it was just a year ago, it might be time to consider carving out a position once more in this $19 billion low-risk bond fund.

We will choose IJR, QQQ, VOO and VO from the above equity ETF's

```{r 3b1, echo=FALSE, message=FALSE,warning=FALSE}
library(mosaic)
library(quantmod)
library(foreach)


stockList_p2 = c('QQQ','BND','VOO','AGG','VO','VCSH','TLT','IJR')

#Extract the data from the database
getSymbols(stockList_p2,from='2017-01-01')

for(ticker in stockList_p2) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
#Get Percentage close to close from previous day

all_returns_p2 = cbind(ClCl(QQQa),ClCl(BNDa),ClCl(VOOa),ClCl(AGGa),ClCl(VOa),ClCl(VCSHa),ClCl(TLTa),ClCl(IJRa))

#,
all_returns_p2 = as.matrix(na.omit(all_returns_p2))
#Remove the first column since it's current day - previous day. As a result we get na

pairs(all_returns_p2)

N = nrow(all_returns_p2)
```

* The Equity ETFs are not correlated with the bond ETFs as seen in the graph since its a different asset class itself. 
* The Bond ETFs are not that correlated with themselves as well since bonds are individual stocks with no sector as such and as a result the correlation is not prevalent

```{r 3b2, echo=FALSE, message=FALSE,warning=FALSE}
set.seed(1)
initial_wealth = 100000
sim2 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth_p2 = initial_wealth
  weights = c(0.125,0.125,0.125,0.125,0.125,0.125,0.125,0.125)
  n_days = 20
  wealthtracker_p2 = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns_p2, 1, orig.ids=FALSE)
    holdings = weights * total_wealth_p2
    holdings = holdings + holdings*return.today
    total_wealth_p2 = sum(holdings)
    wealthtracker_p2[today] = total_wealth_p2
  }
  wealthtracker_p2
}

hist(sim2[,n_days], 25,main = 'Histogram of returns for past 20 days for P2S1')

```
* The returns are in the slightly positive side with normal distribution more towards the right side 

```{r 3b3, echo=FALSE, message=FALSE,warning=FALSE}
plot(wealthtracker_p2, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P2S1')
```
* Max returns were reached around day 18

```{r 3b4, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p2 = mean(sim2[,n_days] - initial_wealth)
cat('Mean of profits for P2S1 is: ')
meanReturn_p2
```


```{r 3b5, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p2_1 = quantile(sim2[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 2 and scenario 1 is : ")
var_p2_1
```

* There is lesser value at risk and lesser mean returns than portfolio 1. This is because of the presence of both equity and bond ETFs The higher volatility of stocks relative to bonds is due to the nature of the two types of investments. When you buy stocks, you’re buying ownership in companies (albeit a small share). When you buy bonds, you’re lending money, either to companies or to governments. Because creditors are paid before owners, it’s riskier to own a company than it is to lend money, so the prices of stocks are more sensitive to changes in the economy.Thus bonds have lesser var but lesser returns 


```{r 3b6, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p2= sim2[,n_days]- initial_wealth
(hist(profit_p2,breaks = 30, main='Histogram of profits/Losses for P2S1',xlab="Profit"))
abline(v=var_p2_1,col="red",lwd=3)
abline(v=mean(profit_p2),col="blue",lwd=3)
text(8000,400,"Mean Line")
text(-10500,700,"Var risk Line")

```


**Scenario-2: Assign more weights to high return ETFs**
  
  
  ```{r 3b7, echo=FALSE, message=FALSE,warning=FALSE}
all_returns_p2Df = as.data.frame(all_returns_p2)
meanDf_p2 =  all_returns_p2Df %>% summarise_if(is.numeric, mean)
library(Hmisc)
hist.data.frame(all_returns_p2Df)
```

```{r 3b8, echo=FALSE, message=FALSE,warning=FALSE}
unlistedDf_p2 = data.frame(score = unlist(meanDf_p2))

rowList_p2 = rownames(unlistedDf_p2)
newDf_p2 = as.data.frame(cbind(rowList_p2,unlistedDf_p2))
ggplot(newDf_p2,
       aes(x=rowList_p2,y=score)) +
  geom_bar(stat="identity") + ggtitle("ETF Returns for Portfolio -2") +
  xlab("ETF") + ylab("ETF Return Score") 
```
* IJR,  QQQ, VOO are the better ETFs so we will assign more weights to them and lesser weight to BND and Agg

```{r 3b9, echo=FALSE, message=FALSE,warning=FALSE}
set.seed(1)
initial_wealth = 100000
sim2 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth_p2s2 = initial_wealth
  weights = c(0.2,0.02,0.2,0.03,0.05,0.05,0.05,0.4)
  n_days = 20
  wealthtracker_p2s2 = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns_p2, 1, orig.ids=FALSE)
    holdings = weights * total_wealth_p2s2
    holdings = holdings + holdings*return.today
    total_wealth_p2s2 = sum(holdings)
    wealthtracker_p2s2[today] = total_wealth_p2s2
  }
  wealthtracker_p2s2
}

hist(sim2[,n_days], 25,main = 'Histogram of returns for past 20 days for P2S2')
```

```{r 3b10, echo=FALSE, message=FALSE,warning=FALSE}

plot(wealthtracker_p2s2, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P2S2')
```

```{r 3b11, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p2s2 = mean(sim2[,n_days] - initial_wealth)
cat('Mean of profits for P2S2 is: ')
meanReturn_p2s2
```

```{r 3b12, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p2_s2 = quantile(sim2[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 2 and scenario 2 is : ")
var_p2_s2
```

* Theres not much of a difference in mean return and var but scenario 2 tends to perform better than scenario - 1.

```{r 3b13, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p2s2= sim2[,n_days]- initial_wealth
(hist(profit_p2s2,breaks = 30, main='Histogram of profits/Losses for P2S2',xlab="Profit"))
abline(v=var_p2_s2,col="red",lwd=3)
abline(v=mean(profit_p2s2),col="blue",lwd=3)
text(8000,800,"MeanLine")
text(-15500,700,"VAR Risk Line")

```
* The returns have increased but the var has gone down and the returns are still less than portfolio - 1

**Portfolio-3**
  
  * We will now go for mix of equity, bonds, commodity,real estate and some currency ETF's

* Invesco DB US Dollar Index Bullish Fund (UUP) : This ETF offers exposure to a basket of currencies relative to the U.S. dollar, decreasing in value when the trade-weighted basket strengthens and increasing when the dollar appreciates. It is appropriate for investors seeking to a fund that is inversely correlated to the broad stock market or for those making a bet on a flight to quality so the aim is that it will help offset some losses

* SPDR Gold Shares (GLD) : GLD is one of the most popular ETFs in the world, offering exposure to an asset class that has become increasingly important to the asset allocation process in recent years. GLD can be used in a number of different ways; some may establish short term positions as a way of hedging against equity market volatility, dollar weakness, or inflation. Others may wish to include gold exposure as part of a long-term investment strategy. GLD is a relatively straightforward product; the underlying assets consist of gold bullion stored in secure vaults. As such, the price of this ETF can be expected to move in lock step with spot gold prices. 

* Vanguard Real Estate ETF (VNQ) : The Vanguard Real Estate Trust (VNQ) offers broad exposure to U.S. equity REITs, alongside a small allocation to specialized REITs and real estate firms. Real estate has historically been embraced because of its ability to deliver excess returns during bull markets and for its low correlation with traditional stock and bond investments. REITs might appeal to investors seeking current income, as these trusts must distribute at least 90% of their income to investors. The fund offers an efficient way for investors to gain indirect exposure to real estate prices

* iShares Gold Trust (IAU) : This fund offers exposure to one of the world’s most famous metals, gold. IAU is designed to track the spot price of gold bullion by holding gold bars in a secure vault, allowing investors to free themselves from finding a place to store the metal. While IAU isn’t the most liquid way to gain exposure to gold, it does have among the lowest expense ratios, making it a solid choice for cost-conscious investors.

We will take 2 equity (IJR,QQQ)  and 2 bond ETFS (TLT,Agg) from the above portfolios


```{r 3c1, echo=FALSE, message=FALSE,warning=FALSE}
library(mosaic)
library(quantmod)
library(foreach)


stockList_p3 = c('QQQ','UUP','GLD','AGG','VO','VNQ','IAU','IJR')

#Extract the data from the database
getSymbols(stockList_p3,from='2017-01-01')

for(ticker in stockList_p3) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}
#Get Percentage close to close from previous day

all_returns_p3 = cbind(ClCl(QQQa),ClCl(UUPa),ClCl(GLDa),ClCl(AGGa),ClCl(VOa),ClCl(VNQa),ClCl(IAUa),ClCl(IJRa))

#,
all_returns_p3 = as.matrix(na.omit(all_returns_p3))
#Remove the first column since it's current day - previous day. As a result we get na

pairs(all_returns_p3)

N = nrow(all_returns_p3)
```

* Due to the different asset classes, there is not much correlation between the ETF's

```{r 3c2, echo=FALSE, message=FALSE,warning=FALSE}
 set.seed(1)
initial_wealth = 100000
sim3 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth_p3 = initial_wealth
	weights = c(0.125,0.125,0.125,0.125,0.125,0.125,0.125,0.125)
	n_days = 20
	wealthtracker_p3 = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns_p3, 1, orig.ids=FALSE)
	  holdings = weights * total_wealth_p3
		holdings = holdings + holdings*return.today
		total_wealth_p3 = sum(holdings)
		wealthtracker_p3[today] = total_wealth_p3
	}
	wealthtracker_p3
}

hist(sim3[,n_days], 25,main = 'Histogram of returns for past 20 days for P3S1',xlab='Holdings')

```

```{r 3c3, echo=FALSE, message=FALSE,warning=FALSE}
plot(wealthtracker_p3, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P3S1')
```

```{r 3c4, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p3s1 = mean(sim3[,n_days] - initial_wealth)
cat('Mean of profits for P3S1 is: ')
meanReturn_p3s1
```

```{r 3c5, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p3_s1 = quantile(sim3[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 3 and scenario 1 is : ")
var_p3_s1
```

```{r 3c6, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p3s1= sim3[,n_days]- initial_wealth
(hist(profit_p3s1,breaks = 30, main='Histogram of profits/Losses for P3S1',xlab="Profit"))
abline(v=var_p3_s1,col="red",lwd=3)
abline(v=mean(profit_p3s1),col="blue",lwd=3)
text(6000,800,"MeanLine")
text(-10500,700,"VAR Risk Line")

```

* The returns are slightly better than portfolio-2 but still less than portfolio - 1 since more returns are obtained for equity ETF's


**Scenario-2 : Assign weights to high performing ETF**
  
  ```{r 3c7, echo=FALSE, message=FALSE,warning=FALSE}
all_returns_p3Df = as.data.frame(all_returns_p3)
meanDf_p3 =  all_returns_p3Df %>% summarise_if(is.numeric, mean)
library(Hmisc)
hist.data.frame(all_returns_p3Df)
```

```{r 3c8, echo=FALSE, message=FALSE,warning=FALSE}
unlistedDf_p3 = data.frame(score = unlist(meanDf_p3))

rowList_p3 = rownames(unlistedDf_p3)
newDf_p3 = as.data.frame(cbind(rowList_p3,unlistedDf_p3))
ggplot(newDf_p3,
       aes(x=rowList_p3,y=score)) +
  geom_bar(stat="identity") + ggtitle("ETF Returns for Portfolio -3") +
  xlab("ETF") + ylab("ETF Return Score") 
```
* We will assign more weight to IJR, QQQ and Voa and less weight to Agg and UUP

```{r 3c9, echo=FALSE, message=FALSE,warning=FALSE}
set.seed(1)
initial_wealth = 100000
sim3 = foreach(i=1:5000, .combine='rbind') %do% {
  total_wealth_p3s2 = initial_wealth
  weights = c(0.02,0.05,0.05,0.4,0.3,0.03,0.05,0.1)
  n_days = 20
  wealthtracker_p3s2 = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns_p3, 1, orig.ids=FALSE)
    holdings = weights * total_wealth_p3s2
    holdings = holdings + holdings*return.today
    total_wealth_p3s2 = sum(holdings)
    wealthtracker_p3s2[today] = total_wealth_p3s2
  }
  wealthtracker_p3s2
}

hist(sim3[,n_days], 25,main = 'Histogram of returns for past 20 days for P3S2',xlab='Holdings')

```

```{r 3c10, echo=FALSE, message=FALSE,warning=FALSE}
plot(wealthtracker_p3s2, type='l',xlab='Days','ylab'='Total Wealth',main='Wealth change in 20 day window for P3S2')
```

```{r 3c11, echo=FALSE, message=FALSE,warning=FALSE}
meanReturn_p3s2 = mean(sim3[,n_days] - initial_wealth)
cat('Mean of profits for P3S2 is: ')
meanReturn_p3s2
```

```{r 3c12, echo=FALSE, message=FALSE,warning=FALSE}
# 5% value at risk:
var_p3_s2 = quantile(sim3[,n_days]- initial_wealth, prob=0.05)
cat("Var for 5% return for Portfolio - 3 and scenario 2 is : ")
var_p3_s2
```
* The mean return is still less even though Var is lesser compared to Portfolio-1. This is due to the fact that equity ETFs can be more profitable due to their volatile nature and the increased market capitalization


```{r 3c13, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
profit_p3s2= sim3[,n_days]- initial_wealth
(hist(profit_p3s2,breaks = 30, main='Histogram of profits/Losses for P3S2',xlab="Profit"))
abline(v=var_p3_s2,col="red",lwd=3)
abline(v=mean(profit_p3s2),col="blue",lwd=3)
text(4000,600,"MeanLine")
text(-8500,700,"VAR Risk Line")
```



```{r 3c14, echo=FALSE, message=FALSE,warning=FALSE}
portfolios = c('P1S1','P1S2','P2S1','P2S2','P3S1','P3S2')
returns = c(meanReturn_p1,meanReturn_p1s2,meanReturn_p2,meanReturn_p2s2,meanReturn_p3s1,meanReturn_p3s2)
returnsDf = data.frame(Portfolio=portfolios,Returns=returns)

ggplot(returnsDf,aes(x=Portfolio,y=Returns)) + geom_bar(stat = "identity") + ggtitle('Mean Profit for Portfolios')
```
* To summarize the mean returns for Portfolio-1, scenario - 2 are desirable when we assign more weight to IJR and QQQ ETFs. Portfolio - 1 gives more returns since equity ETFs give higher returns compared to other asset class as there are higher risk involved as seen in the below graph.

```{r 3c15, echo=FALSE, message=FALSE,warning=FALSE}

vars = c(var_p1,var_p1s2,var_p2_1,var_p2_s2,var_p3_s1,var_p3_s2)
varDf = data.frame(Portfolio=portfolios,var_pct=vars)

ggplot(varDf,aes(x=Portfolio,y=var_pct)) + geom_bar(stat = "identity") + ggtitle('Var for Portfolios')
```
* Because bond ETFs never mature, they never offer the same protection for your initial investment the way that individual bonds can. In other words, you aren't guaranteed to get your money back at some point in the future. You can lose money if interest rates rise. Interest rates change over time. With so many incidents happening in the past 5 years like Covid, Russia-Ukraine War, inflation, it makes sense that with rising interest rates bonds give lesser returns as compared to ETFs.

**As they say, High Risk means High Rewards**
